\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-28 Paper/Paper.tex
Write data preparation

	The data preparation process is shown in Fig.~\ref{fig:A_data_prep}. First,

	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV               &2984&/  &/ &/ &2984\\
					CSC               &/   &102&32&/ &134 \\
					DME               &2500&/  &/ &/ &2500\\
					Drusen            &2500&/  &/ &/ &2500\\
					ERM               &/   &/  &/ &19&19  \\
					Intraretinal&1097&/  &/ &/ &1097\\
					MH                &/   &99 &31&/ &130 \\
					Mactel            &/   &/  &29&/ &29  \\
					Normal            &5000&/  &/ &/ &5000\\
					RP                &/   &102&31&/ &133 \\
					Stargardt         &/   &/  &23&/ &23  \\
					Subretinal  &1083&/  &/ &/ &1083\\
					\bottomrule
				\end{longtable}

@@

				\vspace{0.5cm}
			}
		}
	\end{minipage}
	\begin{minipage}[t]{0.6\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccccc}
					\caption{Fundus abnormities}
					\label{tb:Fundus_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&5&6&\\
					\midrule
					Cotton  &/  &/ &/ &33 &205&/ &238\\
					Drusen            &/  &/ &/ &50 &/  &/ &50 \\     
					Hard    &20 &/ &/ &75 &284&/ &379\\ 
					Hemorrhage        &13 &66&/ &105&278&/ &462\\     
					MH                &/  &/ &/ &/  &/  &34&34 \\        
					Micro   &55 &/ &/ &1  &219&/ &275\\
					Normal            &100&37&15&/  &/  &/ &152\\      
					RP                &/  &22&/ &/  &/  &44&66 \\         
					Vascular&/  &64&/ &14 &/  &/ &78 \\

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN selection rate}
				\label{tb:cycleGAN_selection_rate}\\
				\toprule
				Abnormity&Original&Generated&Selected&Selection Rate\\
				\midrule
				CSC      &134&1730&3000&57.667\% \\
				ERM      &19 &1931&3000&64.367\% \\
				MH       &130&1811&3000&60.367\% \\
				Mactel   &29 &1900&3000&63.333\% \\
				RP       &133&1923&3000&64.100\% \\
				Stargardt&23 &2582&3000&86.067\% \\
				\bottomrule
			\end{longtable}
		}
	}

	TEXT: CycleGAN
	selection criteria
	Why I did not GAN Fundus

@@

	Table: abnormities with description (edit the two tables below)

>>>>

	The data preparation process is shown in Fig.~\ref{fig:A_data_prep}.

	First, we acquire data from publicly available online datasets. For abnormities that we have no data of, we search for images on Google Image. The numbers of images acquired from each data source are shown in Tables \ref{tb:OCT_source} and \ref{tb:Fundus_source}.

	\begin{minipage}[t]{0.4\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccc}
					\caption{OCT abnormities}
					\label{tb:OCT_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{4}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&\\
					\midrule
					CNV    &2984&/  &/ &/ &2984\\
					CSC    &/   &102&32&/ &134 \\
					DME    &2500&/  &/ &/ &2500\\
					Drusen &2500&/  &/ &/ &2500\\
					ERM    &/   &/  &/ &19&19  \\
					IF     &1097&/  &/ &/ &1097\\
					MH     &/   &99 &31&/ &130 \\
					Mactel &/   &/  &29&/ &29  \\
					Healthy&5000&/  &/ &/ &5000\\
					RP     &/   &102&31&/ &133 \\
					ST     &/   &/  &23&/ &23  \\
					SF     &1083&/  &/ &/ &1083\\
					\bottomrule
				\end{longtable}

@@

				\vspace{0.5cm}
			}
		}
	\end{minipage}
	\begin{minipage}[t]{0.6\linewidth}
		{
			\fontsize{9}{12}\selectfont
			{
				\begin{longtable}{cccccccc}
					\caption{Fundus abnormities}
					\label{tb:Fundus_source}\\
					\toprule
					\multirow{2}{*}{Abnormity}&\multicolumn{6}{c}{Source}&\multirow{2}{*}{Total}\\
					&1&2&3&4&5&6&\\
					\midrule
					CWP    &/  &/ &/ &33 &205&/ &238\\
					Drusen &/  &/ &/ &50 &/  &/ &50 \\     
					HE     &20 &/ &/ &75 &284&/ &379\\ 
					HM     &13 &66&/ &105&278&/ &462\\     
					MH     &/  &/ &/ &/  &/  &34&34 \\        
					MA     &55 &/ &/ &1  &219&/ &275\\
					Healthy&100&37&15&/  &/  &/ &152\\      
					RP     &/  &22&/ &/  &/  &44&66 \\         
					VA     &/  &64&/ &14 &/  &/ &78 \\

@@

	Then, for OCT images that have less than 1000 images, we use Cycle-GAN to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy images to abnormity images, and use it to generate new abnormity images. We manually eliminate generated images that look obviously wrong. The elimination rate is shown in Table~\ref{tb:cycleGAN_number}. We only used Cycle-GAN to generate OCT images because generated fundus images are too blurry and do not display the target abnormities.

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN elimination rate}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Eliminated&Elimination Rate\\
				\midrule
				CSC   &134&3000&1270&42.333\% \\
				ERM   &19 &3000&1069&35.633\% \\
				MH    &130&3000&1189&39.633\% \\
				Mactel&29 &3000&1100&36.667\% \\
				RP    &133&3000&1077&36.900\% \\
				ST    &23 &3000&418 &13.933\% \\
				\bottomrule
			\end{longtable}
		}
	}

@@

	Table: abnormities with description (edit the two tables below; ALPHABETICAL ORDER!!!)
